### 2015-11-03 PrincipiaMetaphysicaAutomationPart1/doc/document/TheoryOfAbstractObjectsV1.tex
further additions

\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ Term\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}{\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline
\ isForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\ isPropForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isPropForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\ isTerm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isTerm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Term\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\ isError\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}{\isacharprime}a\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isError\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline

@@

\ countersatifiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline

@@

\ mkTerm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isachardot}t{\isachardot}\ {\isasymequiv}\ Term\ t{\isachardoublequoteclose}%
\isamarkupsection{Some basic tests%
Example signature; entities and relations%

@@

\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%

@@

\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{oops}\isamarkupfalse%

@@

\ {\isacharparenleft}simp{\isacharparenright}%

@@

\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%

@@

\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{done}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharcomma}F{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%

@@

\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}F{\isachardot}\ {\isacharsemicolon}F{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ {\isacharparenleft}simp{\isacharparenright}\ \isacommand{by}\isamarkupfalse%
\ auto\isanewline

>>>>

\ isWff\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isWff\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}\ Term\ {\isasympsi}\ {\isasymRightarrow}\ False\ {\isacharbar}{\isacharunderscore}\ {\isasymRightarrow}\ True{\isachardoublequoteclose}\isanewline
\ isForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Form\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\ isPropForm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isPropForm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ PropForm\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\ isTerm\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isTerm\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Term\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline
\ isError\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}isError\ {\isasymphi}\ {\isasymequiv}\ case\ {\isasymphi}\ of\ Error\ {\isasympsi}\ {\isasymRightarrow}\ True\ {\isacharbar}\ {\isacharunderscore}\ {\isasymRightarrow}\ False{\isachardoublequoteclose}\isanewline

@@

\ countersatisfiable\ {\isacharcolon}{\isacharcolon}\ {\isachardoublequoteopen}io\ opt{\isasymRightarrow}bool{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymphi}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymequiv}\ \ case\ {\isasymphi}\ of\ \isanewline

@@

\ mkTerm\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isachardot}t{\isachardot}\ {\isasymequiv}\ Term\ t{\isachardoublequoteclose}\ \isanewline
\ mkError\ {\isacharcolon}{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharprime}a{\isasymRightarrow}{\isacharprime}a\ opt{\isachardoublequoteclose}\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharasterisk}t{\isacharasterisk}\ {\isasymequiv}\ Term\ t{\isachardoublequoteclose}%
\isamarkupsection{Some Basic Tests%
\isamarkupsubsection{Meta-Logic%
\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isacharparenright}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{by}\isamarkupfalse%
\ \isanewline
\ {\isachardoublequoteopen}{\isacharparenleft}{\isasymforall}{\isasymphi}{\isachardot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isacharparenright}\ {\isasymlongleftrightarrow}\ {\isacharbrackleft}{\isasymforall}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{by}\isamarkupfalse%
\isamarkupsubsection{Verifying Modal Logic Principles%
Necessitation holds%
\ necessitation{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\ {\isasymlongrightarrow}\ {\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ necessitation{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\ {\isasymlongrightarrow}\ {\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
Modal Collapse does not hold%
\ modalCollapse{\isacharunderscore}PropForm{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp%
\ modalCollapse{\isacharunderscore}Form{\isacharcolon}\ \ \ \ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp%
\isamarkupsubsection{S5 Principles%
\ axiom{\isacharunderscore}T{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ axiom{\isacharunderscore}T{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ axiom{\isacharunderscore}B{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ axiom{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ axiom{\isacharunderscore}D{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ axiom{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{by}\isamarkupfalse%
\ axiom{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{by}\isamarkupfalse%
\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ axiom{\isacharunderscore}{\isadigit{5}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ test{\isacharunderscore}A{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ test{\isacharunderscore}A{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ test{\isacharunderscore}B{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{by}\isamarkupfalse%
\ test{\isacharunderscore}B{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{by}\isamarkupfalse%
\ test{\isacharunderscore}C{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp%
\ test{\isacharunderscore}C{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymbox}\ {\isacharparenleft}{\isasymdiamond}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp%
\ test{\isacharunderscore}D{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ test{\isacharunderscore}D{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymdiamond}\ {\isacharparenleft}{\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isasymbox}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\isamarkupsubsection{Validity, Satisfiabilty, Countersatisfiability and Invalidity%
\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
For Terms and Error objects these correspondences do not apply%
\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isachardot}{\isasymphi}{\isachardot}{\isacharbrackright}\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isachardot}{\isasymphi}{\isachardot}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isachardot}{\isasymphi}{\isachardot}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isachardot}{\isasymphi}{\isachardot}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharasterisk}{\isasymphi}{\isacharasterisk}{\isacharbrackright}\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharasterisk}{\isasymphi}{\isacharasterisk}{\isacharbrackright}\isactrlsup c\isactrlsup s\isactrlsup a\isactrlsup t{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharasterisk}{\isasymphi}{\isacharasterisk}{\isacharbrackright}\isactrlsup s\isactrlsup a\isactrlsup t\ {\isasymlongleftrightarrow}\ {\isasymnot}\ {\isacharbrackleft}{\isacharasterisk}{\isasymphi}{\isacharasterisk}{\isacharbrackright}\isactrlsup i\isactrlsup n\isactrlsup v{\isachardoublequoteclose}\ \isacommand{nitpick}\isamarkupfalse%
\isamarkupsubsection{Example signature; entities and relations%

@@

\ simp\ \isacommand{done}\isamarkupfalse%

@@

\ simp\ \isacommand{oops}\isamarkupfalse%

@@

\ simp%

@@

\ simp\ \isacommand{by}\isamarkupfalse%

@@

\ simp\ \isacommand{done}\isamarkupfalse%
\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{by}\isamarkupfalse%

@@

\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymexists}{\isacharparenleft}{\isasymlambda}{\isasymphi}{\isachardot}\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{by}\isamarkupfalse%
\isamarkupsection{Axioms%
\isamarkupsubsection{Axioms for Negations and Conditionals%
\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasympsi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymchi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{2}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharsemicolon}{\isasympsi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymchi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasympsi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymchi}{\isacharsemicolon}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isasymnot}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasympsi}{\isacharcomma}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\ a{\isadigit{2}}{\isadigit{1}}{\isacharunderscore}{\isadigit{3}}{\isacharunderscore}F{\isacharcolon}\ \ {\isachardoublequoteopen}{\isacharbrackleft}{\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isasymnot}\isactrlsup z\ {\isacharsemicolon}{\isasympsi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasympsi}{\isacharsemicolon}{\isacharparenright}\ {\isasymrightarrow}\isactrlsup z\ {\isacharsemicolon}{\isasymphi}{\isacharsemicolon}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
\isamarkupsubsection{Axioms of Identity%
todo%
\isamarkupsubsection{Axioms of Quantification%
todo%
\isamarkupsubsection{Axioms of Actuality%
\ a{\isadigit{3}}{\isadigit{1}}{\isacharunderscore}{\isadigit{1}}{\isacharunderscore}PF{\isacharcolon}\ {\isachardoublequoteopen}{\isacharbrackleft}{\isasymA}\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}\ {\isasymequiv}\isactrlsup z\ {\isacharparenleft}{\isasymnot}\isactrlsup z\ {\isacharparenleft}{\isasymA}\ {\isacharcomma}{\isasymphi}{\isacharcomma}{\isacharparenright}{\isacharparenright}{\isacharbrackright}{\isachardoublequoteclose}%
\ simp\ \isacommand{done}\isamarkupfalse%
